Biotic invasions fuck with the manageability of pollination networks

### 2017-01-17 paper/draft_2.Rmd
Change size of vertex in figure 1 and 2

as_net %>% 
	plot(layout = lay, 
			 vertex.color = v_c, 
			 vertex.size = 30,
			 vertex.label = sp_names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma)

@@

		as_net %>% 
			plot(layout = lay, 
					 vertex.size = 30,
					 vertex.label = names_fancy,
					 vertex.label.family = fam,
					 vertex.label.color = l_c,
					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
					 # vertex.shape = igraph::V(.)$vertex.shape,
					 vertex.color = pal[igraph::V(.)$matched],
					 edge.color = pal[E(.)$matched],
					 edge.label = NA, 
					 edge.width = E(.)$matched/2,
					 edge.label.family = fam,
					 edge.label.color = igraph::E(.)$matched,
					 edge.label.cex = l_s,
					 edge.curved = F,
					 edge.arrow.size = 0.5,
					 margin = ma) %>% 
			print()

@@

plot.new()
legend(0.16, 0.9, legend = c("unmatched link", "matched link"), horiz = TRUE,
			 lty = 1, 
			 col = pal[c(2, 4)],
			 lwd = 2, cex = 0.9, xjust=0.5, yjust=1, bty = "n")

legend(0.57, 0.9, legend = c("unmatched node", "matched node"), horiz = TRUE,
			 pch = 21, 
			 pt.bg = pal[c(2, 4)],
			 pt.cex = 2,
			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")

legend(1-0.16 + 0.05, 0.9, legend = expression(paste(bold("(bold label)"), " ", "superior nodes")), horiz = TRUE,
			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")

@@

```{r figure 2, echo = F, fig.width = 6.2, fig.height = 1.6, message = F, warning = F, fig.pos = "T", fig.cap = "**Different ways to depict quantitative mutualistic networks**. (a) Pollination networks are typically described by the number of visits between each plant and animal species. (b) Given visitation data, the mutual dependences between interacting species are calculated directly based on the relative visitation frequencies. (c) The relative differences of dependences—the interaction asymmetry—then provide a means to identify the dominant direction of the interspecific effects."}

@@

base_net %>%
	plot(layout = lay, 
			 vertex.color = v_c, 
			 vertex.size = 30,
			 vertex.label = sp_names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label = E(.)$weight, 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 frame = F,
			 margin = ma)
text(label_pos_x, label_pos_y, "a)", adj = c(0,0))

bi_net %>% 
	plot(layout = lay, 
			 vertex.color = v_c, 
			 vertex.size = 30,
			 vertex.label = sp_names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = T,
			 edge.arrow.size = 0.5,
			 margin = ma)
text(label_pos_x, label_pos_y, "b)", adj = c(0,0))

as_net %>% 
	plot(layout = lay, 
			 vertex.color = v_c, 
			 vertex.size = 30,
			 vertex.label = sp_names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma)
text(label_pos_x, label_pos_y, "c)", adj = c(0,0))

>>>>

as_net %>% 
	plot(layout = lay, 
			 vertex.color = v_c, 
			 vertex.size = 35,
			 vertex.label = sp_names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma)

@@

		as_net %>% 
			plot(layout = lay, 
					 vertex.size = igraph::V(.)$superior * 10 + 20,
					 vertex.label = names_fancy,
					 vertex.label.family = fam,
					 vertex.label.color = l_c,
					 vertex.label.cex = igraph::V(.)$superior * 0.1 + 0.9,
					 # vertex.shape = igraph::V(.)$vertex.shape,
					 vertex.color = pal[igraph::V(.)$matched],
					 edge.color = pal[E(.)$matched],
					 edge.label = NA, 
					 edge.width = E(.)$matched/2,
					 edge.label.family = fam,
					 edge.label.color = igraph::E(.)$matched,
					 edge.label.cex = l_s,
					 edge.curved = F,
					 edge.arrow.size = 0.5,
					 margin = ma) %>% 
			print()

@@

plot.new()
legend(0.16, 0.9, legend = c("unmatched link", "matched link"), horiz = TRUE,
			 lty = 1, 
			 col = pal[c(2, 4)],
			 lwd = 2, cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")

legend(0.57, 0.9, legend = c("unmatched node", "matched node"), horiz = TRUE,
			 pch = 21, 
			 pt.bg = pal[c(2, 4)],
			 pt.cex = 2,
			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")

legend(1-0.16 + 0.05, 0.9, legend = expression(paste(bold("  superior node"))), horiz = TRUE,
			 pch = 21, 
			 # pt.bg = pal[c(2, 4)],
			 pt.cex = c(3),
			 cex = 0.9, xjust=0.5, yjust=0.8, bty = "n")

# legend(1-0.16 + 0.05, 0.9, legend = expression(paste(bold("(bold label)"), " ", "superior nodes")), horiz = TRUE,
# 			 cex = 0.9, xjust=0.5, yjust=1, bty = "n")

@@

```{r figure 2, echo = F, fig.width = 6.2, fig.height = 1.6, message = F, warning = F, fig.pos = "T", fig.cap = "**Different ways to depict quantitative mutualistic networks**. (a) Pollination networks are frequently described by the observed number of visits between each plant and animal species. (b) Based on that visitation data, the mutual dependences between interacting species are calculated directly based on the relative visitation frequencies. (c) The relative differences of these  dependences—the interaction asymmetry—then provide a means to estimate the dominant direction of the interspecific effects."}

@@

base_net %>%
	plot(layout = lay, 
			 vertex.color = v_c, 
			 vertex.size = 35,
			 vertex.label = sp_names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label = E(.)$weight, 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 frame = F,
			 margin = ma)
text(label_pos_x, label_pos_y, "a)", adj = c(0,0))

bi_net %>% 
	plot(layout = lay, 
			 vertex.color = v_c, 
			 vertex.size = 35,
			 vertex.label = sp_names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = T,
			 edge.arrow.size = 0.5,
			 margin = ma)
text(label_pos_x, label_pos_y, "b)", adj = c(0,0))

as_net %>% 
	plot(layout = lay, 
			 vertex.color = v_c, 
			 vertex.size = 35,
			 vertex.label = sp_names_fancy,
			 vertex.label.family = fam,
			 vertex.label.color = l_c,
			 edge.label = round(E(.)$weight,1), 
			 edge.label.family = fam,
			 edge.label.color = l_c,
			 edge.label.cex = l_s,
			 edge.curved = F,
			 edge.arrow.size = 0.5,
			 margin = ma)
text(label_pos_x, label_pos_y, "c)", adj = c(0,0))
